Why a digital tax may be the only sustainable solution

### 2019-07-27 writing/shortNote/shortnote.tex
Changed short note text.

>>>>

\section{Side Notes}
Since we are now using a physical distance instead of an ordinal distance, when $\lambda$ is high, the transaction cost can be more important than the cost-per-unit in determining profit and relative fitness of firms.

In addition, our model may not be an accurate descriptor of how a tech company works, as it would seem more accurate for tech companies to have a very low or no per-unit-costs, instead having high fixed costs.
